---
title: "Introduction to data visualisation with `ggplot2`"
author: "Ben Matthews"
date: "05/06/2020"
output: 
  xaringan::moon_reader:
    css: xaringan-themer.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_solarized_light()
```

# Welcome!

- What we're going to cover

- Course outline: https://github.com/benmatthewsed/ui-data-visualization-course/blob/master/course_outline.md

- Who we are

- Code of conduct


---

# House rules

- Ask questions whenever `r emo::ji('thumbsup')`
- You can do this through the Blackboard chat facility {demo this now}
- We've structured the sessions with regular breaks, but if you need to leave just leave!
- Materials will live online somewhere so you can catch up later on
- "You're not working from home, you're at home during a crisis trying to work" -- Abraham Lincoln



---

# Who you are

- Why this course?
- What do you want to achieve?


