---
title: "Smooths, transforms and densities"
author: "Ben Matthews"
date: "12/06/2020"
output: 
  xaringan::moon_reader:
    css: xaringan-themer.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_solarized_light()
```

class: center, middle, inverse

# Three types of `geom` layer

---

# Three types of `geom`

- I like to think of `geom`s as being one of three types:
- `geom`s that plot each datum for you
- `geom`s that plot summaries of your dataset for you
- `geom`s that plot things that aren't in your dataset (like reference lines and such)

---

# Plot my data please

- `geom_point`
- `geom_line`
- `geom_bar` (sort of)
- `geom_errorbar` (sort of)
- `geom_tile`
- `geom_sf()` (we'll come back to this in the next session)


---

# Plot a summary of my data

- Univariate/distributions:
    - `geom_histogram`
    - `geom_density`
    - `geom_violin`
- Bivariate:
    - `geom_smooth`
    - `geom_contour`
    
---

# Live coding


---
class: center, middle, inverse

# Ask yourself - do you want to plot your data? A summary of your data? 
# ...Or both?
