---
title: "Types of `geom`"
author: "Ben Matthews"
date: "12/06/2020"
output: 
  xaringan::moon_reader:
    css: xaringan-themer.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_solarized_light()
```

class: center, middle, inverse

# Three types of `geom` layer

---

# Three types of `geom`

- I like to think of `geom`s as being one of three types:
- `geom`s that plot each datum for you
- `geom`s that plot summaries of your dataset for you
- `geom`s that plot things that aren't in your dataset (like reference lines and such); often metadata
- (The official `ggplot` book uses a [slightly different classification system](https://ggplot2-book.org/toolbox.html) for `geom`s)

---

# Plot each datum please

- Make a mark on the plot for __each row__ in the dataset

    - `geom_point`
    - `geom_line`
    - `geom_bar` (sort of)
    - `geom_errorbar` (sort of)
    - `geom_tile`
    - `geom_sf()` (we'll come back to this in the next session)
    - `geom_text()` (sometimes)


---

# Plot a summary of my data please

- Plot something that summarises all/groups of the data in my datset

- Univariate/distributions:
    - `geom_histogram`
    - `geom_density`
    - `geom_violin`
- Bivariate:
    - `geom_smooth`
    - `geom_contour`
    
    
---

# Plot something else on my graph

- Reference lines
    - `geom_vline`
    - `geom_hline`
    - `geom_abline`

- Annotations
    - `geom_text()` (sometimes)

---

# Live coding


---
class: center, middle, inverse

# Ask yourself - do you want to plot your data? A summary of your data? 
# ...Or both?
