---
title: "Recap"
author: "Ben Matthews"
date: "12/06/2020"
output: 
  xaringan::moon_reader:
    css: xaringan-themer.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_solarized_light()
```

# Recap


---

# What is `ggplot2`?

- It's an `R` package that draws graphs, developed by [Hadley Wickham](http://hadley.nz/)

- From the [tidyverse website](https://ggplot2.tidyverse.org/): "`ggplot2` is a system for __declaratively__ creating graphics, based on The Grammar of Graphics. You provide the data, tell `ggplot2` how to map variables to aesthetics, what [visual marks to use to represent data points], and it takes care of the details." 

- ... and what's the Grammar of Graphics? Our `ggplot2` [cheat sheet](https://github.com/rstudio/cheatsheets/raw/master/data-visualization-2.1.pdf) says this is "the idea that you can __build every graph from the same components__: a data set, a coordinate system, and `geom`s—visual marks that represent data points." 

---

class: center, middle, inverse

- Aids perception
- Is powerful
- Is popular


---

class: center, middle, inverse


# Dataset + 
# _mapping_ variables in the dataset to `aes`thetic + 
# Layers of `geom`s (symbols to represent data) = 
# Plot


---

# Three types of `geom`

- `geom`s that plot each datum for you
- `geom`s that plot summaries of your dataset for you
- `geom`s that plot things that aren't in your dataset (like reference lines and such)


---

- Design your data viz with your audience in mind
- Use best practice: design graphs that are easy to understand

---

- Errors are going to happen and that's fine!


---

# In the next session

- The fun stuff!
- Maps
- Beautifying your ggplots
- Answering any questions you have between now and then
- Please feel free to bring your own data!






---

# Optional homework

- Try out this week's [#TidyTuesday](https://github.com/rfordatascience/tidytuesday) challenge



