---
title: "Publication ready plots"
author: "Ben Matthews and Eilidh Jack"
date: "12/06/2020"
output: 
  xaringan::moon_reader:
    css: xaringan-themer.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_solarized_light()
```

---

# Themes

- `theme()` is a bit `r emo::ji("scream")`


- changing the theme

- scales

- If you want to change the theme with `theme_{whatever}` AND adjust
properties settings with `theme()` the call to `theme_{whatever}` __must come first!__


---
# `theme()`
- moving guides
- `legend.position="bottom"`

- rotating axis labels
- `axis.text.x = element_text(angle = 45, hjust = 1)`

---

# Scales

- See https://scales.r-lib.org/


---

# Saving the plot

- Throughout the session we've just let plots print out in the plots pane
- Not so convenient if you want to show someone else your work!

- `ggsave()`
- `filename = `
- `plot = `
- type = "cairo-png"
- height = 
- width = 